### 2014-01-02 Docs/compilers/compilers.tex
renname docs Docs
update for Cray 8.2.x

\begin{itemize}
\item Cray 8.0.2 compiles and runs \maestro\ fine on the interlagos/jaguarpf 
machine at OCLF.
\item Cray 5.12 compiles and runs \maestro\ fine on hopper (8/21/12).
\end{itemize}

>>>>

\begin{itemize}
\item Cray 8.0.2 compiles and runs \maestro\ fine on the interlagos/jaguarpf 
machine at OCLF.
\item Cray 8.0.7 compiles and runs \maestro\ fine on hopper (08/21/12).
\item Cray 8.2.1 and 8.2.2 seem to have issues with OpenMP on hopper (01/02/14).  Basically, in the initial divu iters, we appear to hang.  Compiling in debug mode works fine, but is slow.  This suggests that there is a compiler bug.
\end{itemize}
